---
title: "Mink Analysis"
output: html_notebook
author: "Ann-Kathrin Pohle"
---

This document contains the code used for analysing the dataset "mink_november" which can be found here: https://doi.org/10.17617/3.SFXRZN 


```{r}
library(tidyverse)
library(sjPlot)
library(ggplot2)
library(ggsignif)
library(emmeans)
library(cowplot)
library(lme4)
```


```{r load data}
setwd("/Users/ankapohle/Desktop")
mink <- read_delim("mink_november.csv",",", escape_double = FALSE, trim_ws = TRUE, locale=locale(decimal_mark = "."))

#doi for dataframe: https://doi.org/10.17617/3.SFXRZN 
```



```{r revised lm volume}
mink$Category <- factor(mink$Category, levels = c("wild", "farm", "feral")) 
vol_cat_rev <- lm(volcalc_cbl3 ~ sex+Category, data = mink)
summary(vol_cat_rev)
pairwise <- emmeans(vol_cat_rev, pairwise ~ sex+Category)
tab_model(vol_cat_rev, digits = 5)#, file = "vol_table_revisions.doc")

vol_cat_rev_null <- lm(volcalc_cbl3 ~ sex, data = mink)
vol_cat <- lm(volcalc_cbl3 ~ sex*Category, data = mink)
anova(vol_cat_rev, vol_cat_rev_null)
AIC(vol_cat_rev, vol_cat_rev_null, vol_cat)


#optional and a sanity check
install.packages("AICcmodavg")
library(AICcmodavg)
models <- list(vol_cat_rev, vol_cat_rev_null)
model.names <- c("vol_cat_rev", "vol_cat_rev_null")
aictab(cand.set = models, modnames = model.names)
```


```{r revised lm bh}
bh_cat_rev <- lm(BH.CBL ~ sex + Category, data = mink)
summary(bh_cat_rev)
emmeans(bh_cat_rev, pairwise ~ sex + Category)
tab_model(bh_cat_rev, digits = 6)#, file = "bh_table_revisions.doc")


bh_cat_rev_null <- lm(BH.CBL ~ sex, data = mink)
summary(bh_cat_rev_null)
emmeans(bh_cat_rev_null, pairwise ~ sex)
bh_cat <- lm(BH.CBL ~ sex*Category, data = mink)
anova(bh_cat_rev, bh_cat_rev_null)
AIC(bh_cat_rev, bh_cat_rev_null)

```


```{r revised lm bw}
bw_cat_rev <- lm(BW.CBL ~ sex + Category, data = mink)
summary(bw_cat_rev)
emmeans(bw_cat_rev, pairwise ~ sex + Category)
tab_model(bw_cat_rev, digits = 5)#, file = "bw_table_revisions.doc")

bw_cat_rev_null <- lm(BW.CBL ~ sex, data = mink)
summary(bw_cat_rev_null)
emmeans(bw_cat_rev_null, pairwise ~ sex)
bw_cat <- lm(BW.CBL ~ sex*Category, data = mink)
anova(bw_cat_rev, bw_cat_rev_null)
AIC(bw_cat_rev, bw_cat_rev_null)
```


```{r revised figure one}
ggplot(data = mink, aes(x=Category, y=volcalc_cbl3, color = sex))+
  geom_violin(trim = FALSE)+
  geom_point(position = position_jitterdodge(dodge.width = 0.9))+
  geom_signif(#
  aes(xmin = 1.0, xmax = 2.0, y_position = 0.007, annotations = "****", group = sex),
  data = subset(mink, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(#
  aes(xmin = 2.0, xmax = 3.0, y_position = 0.006, annotations = "****", group = sex),
  data = subset(mink, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(#
  aes(xmin = 1.0, xmax = 3.0, y_position = 0.0075, annotations = "****", group = sex),
  data = subset(mink, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(#male wild - feral
  aes(xmin = 1.0, xmax = 2.0, y_position = 0.0065, annotations = "****", group = sex),
  data = subset(mink, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  geom_signif(#male feral - farm
  aes(xmin = 2.0, xmax = 3.0, y_position = 0.0058, annotations = "****", group = sex),
  data = subset(mink, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  geom_signif(#male wild - feral
  aes(xmin = 1.0, xmax = 3.0, y_position = 0.0075, annotations = "****", group = sex),
  data = subset(mink, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  theme_classic()+
  scale_fill_manual(values=c("#bdbdbd", "#636363"))+
  scale_colour_manual(values=c("#bdbdbd", "#636363"))+
  theme(legend.position = "none")+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("Vol/CBL^3")+labs(x= expression(""), 
                         y= expression("Vol/"*CBL^{3}))+
  facet_wrap("sex", ncol = 2)
```


#####Supplementary Material#####

#####Supplementary Tables#####

Supplementary Table 1 was configured by using the below code to extract median and standard deviation values. The values were manually put into a table in word. To run the code for obtaining medians, subsets were created.

```{r}

target <- c("M")
mink_m <- mink %>%
  filter(sex %in% target)

target <- c("F")
mink_f <- mink %>%
  filter(sex %in% target)


```


```{r medians and SD for Supplementary Table S1}
###CBL####
median(mink_f$CBL[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$CBL[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$CBL[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$CBL[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$CBL[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$CBL[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$CBL[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$CBL[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$CBL[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$CBL[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$CBL[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$CBL[mink_m$Category=="farm"], na.rm=TRUE) 


####Absolute BW####
median(mink_f$BW[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$BW[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$BW[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$BW[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$BW[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$BW[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$BW[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$BW[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$BW[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$BW[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$BW[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$BW[mink_m$Category=="farm"], na.rm=TRUE) 


####Absolute BH####
median(mink_f$BH[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$BH[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$BH[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$BH[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$BH[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$BH[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$BH[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$BH[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$BH[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$BH[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$BH[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$BH[mink_m$Category=="farm"], na.rm=TRUE) 


#####Absolute Vol####
median(mink_f$vol_calc[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$vol_calc[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$vol_calc[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$vol_calc[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$vol_calc[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$vol_calc[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$vol_calc[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$vol_calc[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$vol_calc[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$vol_calc[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$vol_calc[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$vol_calc[mink_m$Category=="farm"], na.rm=TRUE) 


####BW/CBL####
median(mink_f$BW.CBL[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$BW.CBL[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$BW.CBL[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$BW.CBL[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$BW.CBL[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$BW.CBL[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$BW.CBL[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$BW.CBL[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$BW.CBL[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$BW.CBL[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$BW.CBL[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$BW.CBL[mink_m$Category=="farm"], na.rm=TRUE) 


####BH/CBL####
median(mink_f$BH.CBL[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$BH.CBL[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$BH.CBL[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$BH.CBL[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$BH.CBL[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$BH.CBL[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$BH.CBL[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$BH.CBL[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$BH.CBL[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$BH.CBL[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$BH.CBL[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$BH.CBL[mink_m$Category=="farm"], na.rm=TRUE) 


####Vol/CBL^3####
median(mink_f$volcalc_cbl3[mink_f$Category=="feral"], na.rm=TRUE) 
median(mink_m$volcalc_cbl3[mink_m$Category=="feral"], na.rm=TRUE) 
sd(mink_f$volcalc_cbl3[mink_f$Category=="feral"], na.rm=TRUE) 
sd(mink_m$volcalc_cbl3[mink_m$Category=="feral"], na.rm=TRUE) 

median(mink_f$volcalc_cbl3[mink_f$Category=="wild"], na.rm=TRUE) 
median(mink_m$volcalc_cbl3[mink_m$Category=="wild"], na.rm=TRUE) 
sd(mink_f$volcalc_cbl3[mink_f$Category=="wild"], na.rm=TRUE) 
sd(mink_m$volcalc_cbl3[mink_m$Category=="wild"], na.rm=TRUE) 

median(mink_f$volcalc_cbl3[mink_f$Category=="farm"], na.rm=TRUE) 
median(mink_m$volcalc_cbl3[mink_m$Category=="farm"], na.rm=TRUE) 
sd(mink_f$volcalc_cbl3[mink_f$Category=="farm"], na.rm=TRUE) 
sd(mink_m$volcalc_cbl3[mink_m$Category=="farm"], na.rm=TRUE) 

```

Supplementary Tables S2, S3 and S4 were manually configured after manually calculating each value.

Supplementary Table S5 was configured using the below code. This code will compare all possible combinations. To simplify, we only kept and displayed comparisons of interest in our manuscript (E.g. Comparisons such as M feral - M wild were displayed while comparisons such as M feral - F wild were left out). To facilitate readability (larger estimate and CI values), we displayed a table that used values multiplied by 1000.

```{r Supplementary Table S5}
vol_cat2 <- lm(volcbl3_big ~ sex+Category, data = mink)
emmeans(vol_cat, pairwise ~ sex+Category)
```


```{r Supplementary Table S6}
bh_cat2 <- lm(bhcbl_big ~ sex+Category, data = mink)
tab_model(bh_cat2, digits = 2)
```

See description for Supplementary Table S5. 
```{r Supplementary Table S7}
emmeans(bh_cat2, pairwise ~ sex+Category)
```

To facilitate readability (larger estimate and CI values), we displayed a table that used values multiplied by 1000.
```{r Supplementary Table S8}
bw_cat2 <- lm(bwcbl_big ~ sex+Category, data = mink)
tab_model(bw_cat2, digits = 2)
```

See description for Supplementary Table S5.
```{r Supplementary Table S9}
emmeans(bw_cat2, pairwise ~ sex+Category)
```


#####Supplementary Figures#####


Supplementary Figure 1 was created manually outside of R. 

```{r Supplementary Figure S2}

cbl <- ggplot (data = subset(mink, month == c("11")), aes(x=Category, y=CBL))+geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_blank(), axis.title.y = element_text(size = 17))+
  ggtitle("")+
  xlab("")+
  ylab("CBL")
cbl

vol <- ggplot (data = subset(mink, month == c("11")), aes(x=Category, y=vol_calc))+
  geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_blank(), axis.title.y = element_text(size = 17))+
  ggtitle("")+
  xlab("")+
  ylab("Vol")

vol

volbycbl3 <- ggplot (data = subset(mink, month == c("11")), aes(x=Category, y=volcalc_cbl3))+
  geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("Vol/CBL^3")+labs(x= expression(""), 
                         y= expression("Vol/"*CBL^{3}))
volbycbl3


plot_grid(cbl, vol, volbycbl3,
          nrow = 3,  
          align = "hv",
          axis = "l",
          rel_heights = 5,
          labels = c("a", "b", "c"),
          label_size = 15)

```



```{r revised Supplementary Figure S3}
pairwise <- emmeans(vol_cat_rev, pairwise ~ sex+Category)
pairwise.df <- data.frame(pairwise$contrasts)
pairwise.df$new <- pairwise.df$contrast

pairwise.df <- separate(data = pairwise.df, col = new, into = c("first", "second"), sep = "\\-")

ggplot(pairwise.df[pairwise.df$contrast %in% c("F wild - F farm", "F wild - F feral", "F farm - F feral", "M wild - M farm", "M farm - M feral", "M wild - M feral"),], aes(x=estimate*1000, y = second))+ 
  geom_point( aes(x = estimate*1000))+#,ggstance::position_dodgev(height=0.6))+
  geom_linerange(aes(xmin=estimate *1000 - SE *1000, xmax= estimate*1000 + SE*1000))+
                   #ggstance::position_dodgev(height=0.6), aes(xmin=estimate *1000 - SE *1000, xmax= estimate*1000 + SE*1000))+
  geom_vline(xintercept = 0)+
  geom_text(vjust = -0.6, aes(label = first))+
  #geom_text(aes(label = first), size = 3, (position = position_dodge2(width = 0.5), vjust =0.4))+#, vjust = -0.7))+
  scale_x_continuous(breaks=c(-2,-1,0,1,2), limits = c(-2, 2))+ 
  #scale_y_discrete(labels = c("M feral", "M farm", "M feral", "M wild", "F feral", "F farm", "M feral", "M farm", "F feral"))+
  theme_classic()+
  theme(legend.position = "none", axis.text.y=element_text(size=13), axis.text.x = element_text(size = 15), axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  ylab("Intercept")+
  xlab("Estimate")
```



```{r Supplementary Figure S4}
ggplot(data = mink, aes(x=Category, y=BH.CBL, color = sex))+
  geom_violin(trim = FALSE)+
  geom_point(position = position_jitterdodge(dodge.width = 0.9))+
  geom_signif(# female wild - farm
  aes(xmin = 1.0, xmax = 2.0, y_position = 0.375, annotations = "****", group = sex),
  data = subset(mink, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(# female feral - farm
  aes(xmin = 2.0, xmax = 3.0, y_position = 0.380, annotations = "****", group = sex),
  data = subset(mink, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(# female wild- feral
  aes(xmin = 1.0, xmax = 3.0, y_position = 0.390, annotations = "ns", group = sex),
  data = subset(mink, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.0, color = "#bdbdbd")+
  geom_signif(#male wild - farm
  aes(xmin = 1.0, xmax = 2.0, y_position = 0.385, annotations = "****", group = sex),
  data = subset(mink, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  geom_signif(#male feral - farm
  aes(xmin = 2.0, xmax = 3.0, y_position = 0.375, annotations = "****", group = sex),
  data = subset(mink, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  geom_signif(#male wild - feral
  aes(xmin = 1.0, xmax = 3.0, y_position = 0.395, annotations = "****", group = sex),
  data = subset(mink, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  theme_classic2()+
  scale_fill_manual(values=c("#bdbdbd", "#636363"))+
  scale_colour_manual(values=c("#bdbdbd", "#636363"))+
  theme(legend.position = "none")+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("BH/CBL")+
  facet_wrap("sex", ncol = 2)
```



```{r Revised Supplementary Figure S5 }
pairwise.bh <- emmeans(bh_cat_rev, pairwise ~ sex+Category)
pairwise.bh.df <- data.frame(pairwise.bh$contrasts)
pairwise.bh.df$new <- pairwise.bh.df$contrast

pairwise.bh.df <- separate(data = pairwise.bh.df, col = new, into = c("first", "second"), sep = "\\-")

ggplot(pairwise.bh.df[pairwise.bh.df$contrast %in% c("F wild - F farm", "F wild - F feral", "F farm - F feral", "M wild - M farm", "M farm - M feral", "M wild - M feral"),], aes(x=estimate*1000, y = second))+ 
  geom_point( aes(x = estimate*1000))+#,ggstance::position_dodgev(height=0.6))+
  geom_linerange(aes(xmin=estimate *1000 - SE *1000, xmax= estimate*1000 + SE*1000))+
                   #ggstance::position_dodgev(height=0.6), aes(xmin=estimate *1000 - SE *1000, xmax= estimate*1000 + SE*1000))+
  geom_vline(xintercept = 0)+
  geom_text(vjust = -0.6, aes(label = first))+
  #geom_text(aes(label = first), size = 3, (position = position_dodge2(width = 0.5), vjust =0.4))+#, vjust = -0.7))+
  scale_x_continuous(breaks=c(-20,-10,0,10,20,30), limits = c(-20, 30))+ 
  #scale_y_discrete(labels = c("M feral", "M farm", "M feral", "M wild", "F feral", "F farm", "M feral", "M farm", "F feral"))+
  theme_classic()+
  theme(legend.position = "none", axis.text.y=element_text(size=13), axis.text.x = element_text(size = 15), axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  ylab("Intercept")+
  xlab("Estimate")
```


```{r Supplementary Figure S6}
ggplot(data = minks_nov, aes(x=Category, y=BW.CBL, color = sex))+
  geom_violin(trim = FALSE)+
  geom_point(position = position_jitterdodge(dodge.width = 0.9))+
  geom_signif(# female wild - farm
  aes(xmin = 1.0, xmax = 2.0, y_position = 0.490, annotations = "****", group = sex),
  data = subset(minks_nov, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(# female feral - farm
  aes(xmin = 2.0, xmax = 3.0, y_position = 0.510, annotations = "****", group = sex),
  data = subset(minks_nov, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#bdbdbd")+
  geom_signif(# female wild- feral
  aes(xmin = 1.0, xmax = 3.0, y_position = 0.515, annotations = "ns", group = sex),
  data = subset(minks_nov, sex %in% "F"), manual = TRUE, tip_length = 0.01, vjust = 0.0, color = "#bdbdbd")+
  geom_signif(#male wild - farm
  aes(xmin = 1.0, xmax = 2.0, y_position = 0.505, annotations = "****", group = sex),
  data = subset(minks_nov, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  geom_signif(#male feral - farm
  aes(xmin = 2.0, xmax = 3.0, y_position = 0.500, annotations = "****", group = sex),
  data = subset(minks_nov, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.5, color = "#636363")+
  geom_signif(#male wild - feral
  aes(xmin = 1.0, xmax = 3.0, y_position = 0.513, annotations = "ns", group = sex),
  data = subset(minks_nov, sex %in% "M"), manual = TRUE, tip_length = 0.01, vjust = 0.0, color = "#636363")+
  theme_classic2()+
  scale_fill_manual(values=c("#bdbdbd", "#636363"))+
  scale_colour_manual(values=c("#bdbdbd", "#636363"))+
  theme(legend.position = "none")+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("BW/CBL")+
  facet_wrap("sex", ncol = 2)
```


The values used for the following figure were manually extracted after running each model repeatedly with differing intercepts. The code for changing intercepts and extraction of coefficients and confidence intervals can be found in the file: different_intercept_same_models.Rmd
These values were manually extracted (not including estimates from interactions) and stored in separate data frames, called "vol_models", "bh_models" and "bw_models". 


```{r Revised Supplementary Figure S7}
pairwise.bw <- emmeans(bw_cat_rev, pairwise ~ sex+Category)
pairwise.bw.df <- data.frame(pairwise.bw$contrasts)
pairwise.bw.df$new <- pairwise.bw.df$contrast

pairwise.bw.df <- separate(data = pairwise.bw.df, col = new, into = c("first", "second"), sep = "\\-")

ggplot(pairwise.bw.df[pairwise.bw.df$contrast %in% c("F wild - F farm", "F wild - F feral", "F farm - F feral", "M wild - M farm", "M farm - M feral", "M wild - M feral"),], aes(x=estimate*1000, y = second))+ 
  geom_point( aes(x = estimate*1000))+#,ggstance::position_dodgev(height=0.6))+
  geom_linerange(aes(xmin=estimate *1000 - SE *1000, xmax= estimate*1000 + SE*1000))+
                   #ggstance::position_dodgev(height=0.6), aes(xmin=estimate *1000 - SE *1000, xmax= estimate*1000 + SE*1000))+
  geom_vline(xintercept = 0)+
  geom_text(vjust = -0.6, aes(label = first))+
  #geom_text(aes(label = first), size = 3, (position = position_dodge2(width = 0.5), vjust =0.4))+#, vjust = -0.7))+
  scale_x_continuous(breaks=c(-20,-10,0,10,20,30), limits = c(-25, 35))+ 
  theme_classic()+
  theme(legend.position = "none", axis.text.y=element_text(size=13), axis.text.x = element_text(size = 15), axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  ylab("Intercept")+
  xlab("Estimate")
```



```{r Supplementary Figure S8}

cbl <- ggplot (data = subset(mink, month == c("11")), aes(x=Category, y=CBL))+geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_blank(), axis.title.y = element_text(size = 17))+
  ggtitle("")+
  xlab("")+
  ylab("CBL")

BH <- ggplot (data = subset(mink, month == c("11")), aes(x=Category, y=BH))+
  geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_blank(), axis.title.y = element_text(size = 17))+
  ggtitle("")+
  xlab("")+
  ylab("BH")

vol <- ggplot (data = subset(mink, month == c("11")), aes(x=Category, y=vol_calc))+
  geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  ggtitle("")+
  xlab("")+
  ylab("Vol")

BW <- ggplot(data = subset(mink, month == c("11")), aes(x = Category, y = BW))+
  geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  ggtitle("")+
  xlab("")+
  ylab("BW")

cowplot::plot_grid(cbl, BH, vol, BW,
          align = "v",
          axis = "lr",
          labels = c("a", "b", "c", "d"),
          label_size = 15)

```


```{r Supplementary Figure S9}
bwcbl <- ggplot (data = mink, aes(x=Category, y=BW.CBL))+
  geom_boxplot(aes(fill=sex))+
  theme_classic2()+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_text(size = 20), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("BW/CBL")


volcbl <- ggplot(data = mink, aes(x = Category, y = volcalc_cbl3))+
  geom_boxplot(aes(fill=sex))+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme_classic2()+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_blank(), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("Vol/CBL^3")+labs(x= expression(""), 
       y= expression("Vol/"*CBL^{3}))

bhcbl <- ggplot(data = mink, aes(x = Category, y = BH.CBL))+
  geom_boxplot(aes(fill=sex))+
  scale_colour_manual(values=c("#f0f0f0", "#bdbdbd")) + 
  scale_fill_manual(values=c("#f0f0f0", "#bdbdbd"))+
  theme_classic2()+
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 23))+
  theme(axis.text.y=element_text(size=15), axis.text.x = element_blank(), axis.title.y = element_text(size = 17))+
  xlab("")+
  ylab("BH/CBL")



plot_grid(volcbl, bhcbl, bwcbl,
          nrow = 3,  
          align = "v",
          axis = "lr",
          labels = c("a", "b", "c"),
          label_size = 15)
```

